Towards the near-infrared detection of brown dwarf companions: Exploring methods to detect low mass stellar companions from blended spectra \thanks{Based on observations collected at the European Organisation for Astronomical Research in the Southern Hemisphere under ESO programme 089.C-0977(A)}

### 2019-05-31 nir_companions.tex
small tweaks

% Abstract of the paper
\begin{abstract}
   {\bl In this paper we attempt to directly detect the near-infrared spectrum of candidate brown dwarf (BD) companions around FGK stars to assert or discard their stellar nature. Individual \nir{} spectra are fitted to a synthetic binary model comprised of two PHOENIX-ACES spectra using a \chi squared approach. The observed spectra are wavelength calibrated and corrected for the atmospheric absorption with the aid of synthetic telluric models. This was unable to successfully detect the faint spectra of even the largest companion in the sample. We explore how the companion recovery fitting performs on simulated observations and discuss reasons for the non-detection observed. From the injection-recovery analysis, this technique in its current form, is insufficient to recover a companion below 3800~K which corresponds to an upper mass limit for the companions around \(\rm 600~M_{Jup}\). This work highlights the challenges in the spectral detection of faint companions. We explore the limitations of the companion detection with synthetic models at low companion/host flux ratios below 1 per cent, made difficult by the discrepancy between observed and synthetic spectra around 2100~nm.}
\end{abstract}

@@

\subsection{Future implementation}
\label{subsec:future}
\subsubsection{High resolution instrumentation}
\label{subsubsec:highres}
The future of high resolution near- and mid- IR spectrographs is looking bright, with many new ground- and space-based instruments currently being developed. Notable examples include CARMENES (550--1710~nm, R=82\,000) which is now operational~\citep{quirrenbach_carmenes_2014}, while SPIRou (980--2350~nm, R=73\,500)~\citep{artigau_spirou_2014} and NIRPS (970--1810~nm, R=100\,000)~\citep{bouchy_nearinfrared_2017} are still being assembled and installed. The eagerly awaited \textit{JWST} \citep{gardner_james_2006} will provide observations in both the near-IR (600--5300~nm, R=2700) and mid-IR (4900--28\,800~nm, R$\sim$1550--3250) regions without contamination from our atmosphere.

>>>>

% Abstract of the paper
\begin{abstract}
   {\bl In this paper we attempt to directly detect the near-infrared (nIR) spectrum of candidate brown dwarf (BD) companions around FGK stars to assert or discard their stellar nature. Individual nIR spectra are fitted to a synthetic binary model comprised of two PHOENIX-ACES spectra using a $\chi^2$ approach. The observed spectra are wavelength calibrated and corrected for the atmospheric absorption with the aid of synthetic telluric models. This was unable to successfully detect the faint spectra of even the largest companion in the sample. We explore how the companion recovery fitting performs on simulated observations and discuss reasons for the non-detection observed. From the injection-recovery analysis, this technique in its current form, is insufficient to recover a companion below 3800~K which corresponds to an upper mass limit for the companions around \(\rm 600~M_{Jup}\). This work highlights the challenges in the spectral detection of faint companions. We explore the limitations of the companion detection with synthetic models at low companion/host flux ratios below 1 per cent, made difficult by the discrepancy between observed and synthetic spectra around 2100~nm.}

\end{abstract}

@@

\subsection{Future implementation}
\label{subsec:future}
\subsubsection{High resolution instrumentation}
\label{subsubsec:highres}
The future of high resolution near- and mid- IR spectrographs is looking bright, with many new ground- and space-based instruments currently being developed. Notable examples include CARMENES (550--1710~nm, R=82\,000) which is now operational~\citep{quirrenbach_carmenes_2014}, while SPIRou (980--2350~nm, R=73\,500)~\citep{artigau_spirou_2014} and NIRPS (970--1810~nm, R=100\,000)~\citep{bouchy_nearinfrared_2017} are still being assembled and installed. The eagerly awaited \textit{JWST}~\citep{gardner_james_2006} will provide observations in both the near-IR (600--5300~nm, R=2700) and mid-IR (4900--28\,800~nm, R$\sim$1550--3250) regions without contamination from our atmosphere.
